\section*{1. Sách và giáo trình}
\begin{itemize}
	\item Paul Zimmermann, et al., \textit{Computational Mathematics with SageMath}, Springer, 2018.
	\item William Stein, \textit{Sage for Power Users}, University of Washington, 2011.
	\item Gregory Bard, \textit{Sage for Undergraduates}, American Mathematical Society, 2015.
	\item Robert A. Beezer, \textit{A First Course in Linear Algebra (with Sage)}, University of Puget Sound, 2017.
\end{itemize}

\section*{2. Bài báo và công trình khoa học}
\begin{itemize}
	\item William Stein et al., “Sage: Open Source Mathematical Software,” \textit{Notices of the American Mathematical Society}, 2008.
	\item Nicolas M. Thiéry, “Sage: un logiciel pour les mathématiques libres et collaboratives,” \textit{Gazette des Mathématiciens}, 2007.
	\item P. Zimmermann, “The Design of SageMath,” \textit{Lecture Notes in Computer Science}, Springer, 2016.
	\item Jeroen Demeyer, “The Development of SageMath as an Open Source Project,” \textit{Journal of Open Source Software}, 2019.
	\item Clément Pernet, “High-Performance Linear Algebra with SageMath,” \textit{Journal of Symbolic Computation}, 2020.
\end{itemize}

\section*{3. Nguồn tham khảo trực tuyến}
\begin{itemize}
	\item Trang chủ SageMath: \url{https://www.sagemath.org}
	\item Tài liệu chính thức: \url{https://doc.sagemath.org}
	\item Hệ thống thử nghiệm trực tuyến: \url{https://sagecell.sagemath.org}
	\item Diễn đàn hỗ trợ cộng đồng: \url{https://ask.sagemath.org}
	\item Tài liệu Python: \url{https://docs.python.org}
	\item StackOverflow (chủ đề SageMath và Python): \url{https://stackoverflow.com/questions/tagged/sagemath}
	\item GitHub SageMath: \url{https://github.com/sagemath/sage}
	\item SageMath Wiki: \url{https://wiki.sagemath.org}
	\item SageManifolds: \url{https://sagemanifolds.obspm.fr}
	\item Hướng dẫn sử dụng SageMath trên Math3ma: \url{https://www.math3ma.com/sagemath}
\end{itemize}
